Growing libraries of concepts with wake-sleep program induction

### 2018-07-30 nips_2018_author_response.tex
Added some answers to reviewer 2

>>>>

\subsubsection*{More specific questions}

\paragraph*{Reviewer 2: Origin of list task} All the list tasks were manually
created in order to be interesting, challeging, but also human-interpretable for
a prior behaviour experiment. They pre-existed our algorithm.

\paragraph*{Reviewer 2: assesment of the recognition model} The recognition
model's contribution was measured on lesions blabla
